mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-15 Draft3.Rmd
small changes Table 2

```{r custom-operators, echo=FALSE}
op <- list(cross=quote(x %*% y), dot=quote(x %.% y), kronecker=quote(X %x% Y),
  'integer division'=quote(x %/% y))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))

>>>>

```{r custom-operators, echo=FALSE}
op <- list(cross=quote(x %*% y), dot=quote(x %.% y), kronecker=quote(X %x% Y),
  'integer division'=quote(x %/% y), and=quote(A & B), vel=quote(A | B), xor=quote(xor(A, B)), not=quote(!A))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))
